maxent model avec xvalidation (year-based test training)

### 2019-05-14 src/maxent_avec_xvalidation.Rmd
stoopid merging

```{r}

>>>>

```{r}
mthlst <- c("jan", "mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

for(m in 1:length(mthlst)){
  mthna <- mthlst[m]
  mpabin_lst <- list.files(paste0("../output/maxent/predictions/", mthna), pattern =  "^binary_avg_cloglog.*.asc", full.names = TRUE)

  stdep <- read.csv("../output/maxent/models/dec1998/stack_depth.csv", header = TRUE)
  depthlayers <- data.frame(cbind(unique(stdep$ascdepths)))
  names(depthlayers)[names(depthlayers) == "cbind.unique.stdep.ascdepths.."] <- "depth"
  depthlayers$depth <- as.character(depthlayers$depth)

  for (d in 1:nrow(depthlayers)){
    dep <- depthlayers$depth[d]
    for (a in 1:length(mpabin_lst)){
      asc <- mpabin_lst[a]
      if (grepl(dep, asc)){
        depthlayers[d , paste0("a", colno)] <- asc
          colno <- colno+1
      }
    }
  }
  write.csv(depthlayers, (paste0("../output/maxent/predictions/", mthna, "_binary_avg_asclayerbydepth.csv")), row.names = TRUE)
}

a <- read.csv("../output/maxent/predictions/apr_binary_avg_asclayerbydepth.csv", header = TRUE)
b <- read.csv("../output/maxent/predictions/may_binary_avg_asclayerbydepth.csv", header = TRUE)
c <- merge(a, b, by=0)

data <- rbindlist(lapply(list.files("../output/maxent/predictions/", pattern = ".*binary_avg_asclayerbydepth.csv", full.names = TRUE), fread))
